Local to Global Mariculture Modelling

### 2025-09-04 index.qmd

>>>>

```{r}
#| label: fig-spatial-N-inputs-change
#| fig-height: 12
#| fig-cap: Change in total N inputs per unit biomass of salmon produced when farms are fed the MD feed (top), or the NI feed (bottom) compared to when farms are fed the PD feed.

N_ins_comp <- rbind(
  find_read(data_analysis_path, "P_excr_farm_per_biom_summed"),
  find_read(data_analysis_path, "P_uneat_farm_per_biom_summed")
  ) %>% 
  st_drop_geometry() %>% 
  select(-sd_biom) %>% 
  mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds)) %>% 
  pivot_wider(
    names_from = feed,
    values_from = mean_biom,
    values_fn = drop_units
  ) %>% 
  group_by(country, farm_ID) %>% 
  reframe(
    PD = sum(PD),
    MD = sum(MD), 
    NI = sum(NI)
  ) %>% 
  mutate(MD = (MD-PD),
         NI = (NI-PD)) %>% 
  select(-PD) %>% 
  pivot_longer(
    names_to = "feed",
    values_to = "diff",
    cols = c(MD, NI)
  ) %>% 
  mutate(
    feed = factor(feed, levels = short_feeds),
    feed = droplevels(feed),
    diff = diff %>% set_units("g g_fish-1") %>% set_units("kg t_fish-1") %>% drop_units()
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

p_bigmap_robinson +
  geom_sf(
    data = N_ins_comp, 
    aes(colour = diff, geometry = geometry), 
    size = 2
  ) +
  coord_sf() +
  scale_color_viridis_c(option = "turbo", breaks = seq(10, 35, 5), limits = c(10,36)) + 
  guides(col = guide_colourbar(
    title = expression("Difference in N inputs (kg/t salmon)"),
    direction = "horizontal", position = "bottom",
    label.position = "bottom", title.position = "top",
    title.vjust = 1, title.hjust = 0.5,
    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 1,
    barheight = 1.5, barwidth = 20,
  )) +
  facet_grid(rows = vars(feed)) +
  # prettyplot() +
  theme(strip.background = element_blank(), strip.text = element_blank(),
        axis.title = element_blank(),
        legend.position = "bottom")
```

```{r}
#| label: N-inputs-change-patchwork-map
#| fig-cap: Change in total N inputs per unit biomass of salmon produced when farms are fed the MD feed (A), or the NI feed (B) compared to when farms are fed the PD feed.

p_mercator <- p_bigmap_mercator +
  geom_sf(
    data = N_ins_comp,
    aes(colour = diff, geometry = geometry), 
    size = 2.5
  ) +
  coord_sf() +
  scale_color_viridis_c(option = "turbo", breaks = seq(10, 35, 5), limits = c(10,36)) + 
  guides(col = guide_colourbar(
    title = expression("Difference in N inputs (kg/t salmon)"),
    direction = "horizontal", position = "bottom",
    label.position = "bottom", title.position = "top",
    title.vjust = 1, title.hjust = 0.5,
    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 1,
    barheight = 1.5, barwidth = 20,
  )) +
  prettyplot() +
  theme(
    strip.background = element_blank(), strip.text = element_blank(),
    legend.position = "bottom"
  ) +
  labs(y = "Latitude", x = "Longitude")

facet_labels <- c(
  "MD" = "A",
  "NI" = "B"
)

ins[[1]] + facet_grid(cols = vars(feed), labeller = as_labeller(facet_labels))
ins[[2]] + facet_grid(rows = vars(feed), labeller = as_labeller(facet_labels))
ins[[3]] + facet_grid(cols = vars(feed), labeller = as_labeller(facet_labels))
ins[[4]] + facet_grid(cols = vars(feed), labeller = as_labeller(facet_labels))
ins[[5]] + facet_grid(cols = vars(feed), labeller = as_labeller(facet_labels))
```
